---
title: "Lab 03 - Nobel laureates"
author: "Annie Somerville"
date: "02.10.21"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r glimpse, message=FALSE}
glimpse(nobel)
```
This data has 935 observations/nobel laureates and 26 variables.

### Exercise 2


#### r nobel_living
``` {r nobel_living}
nobel_living <- nobel %>%
  filter (
    is.na(died_date) &
    !is.na(country_original) &
    gender != "org"
  )
glimpse(nobel_living)
```

I used the `r glimpse(nobel_living)` code above to filter for people opposed to organizations, those who are still living, and those who had available countries.

### Exercise 3

``` {r country_us}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```

``` {r nobel_living_science}
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```


``` {r barplot}
ggplot(data=nobel_living_science, aes(x=category, fill=country_us)) +
geom_bar(stat="count", position=position_dodge()) +
  coord_flip()
```

Winners of science prizes were much more likely to be in the US than other countries, so I would say that Buzzfeed's article headline seems accurate.


### Exercise 4

``` {r born_country_us}
nobel_living_science <- nobel_living_science %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )

nobel_living_science %>%
  count(born_country_us)
```

636 of the winners were not born in the US, and 271 winners were born in the US. Out of the science winners, 123 were born outside the US and 105 were born in the US.

### Exercise 5

``` {r born_and_won_us}
nobel_living_science <- nobel_living_science %>%  
  mutate(
    born_and_won_us = case_when(born_country_us == "Other" & country_us == "Other" ~ "Born in Other, Won in Other", #condition 1
                         born_country_us == "Other" & country_us == "USA" ~ "Born in Other, Won in USA", #condition 2
                         born_country_us == "USA" & country_us == "Other" ~ "Born in USA, Won in Other", #condition 3
                         born_country_us == "USA" & country_us == "USA" ~ "Born in USA, Won in USA")) #condition4

nobel_living_science %>%
  count(born_and_won_us)
```

``` {r barplot2}
ggplot(data=nobel_living_science, aes(x=category, group=born_and_won_us, fill=born_and_won_us)) +
geom_bar(stat="count", position="dodge") +
  coord_flip()
```
Buzzfeed's claim definitely seems accurate based on this visualization because there are many people born in other countries who immigrated to the USA and won the nobel prize, thus contributing to American science.

### Exercise 6

``` {r freq-born_country}
nobel_living_science %>% 
  filter(born_and_won_us=="Born in Other, Won in USA") %>%
  count(born_country, sort=TRUE)
```

Both Germany and the UK are the most common countries to have laureates who were born in those countries, but won the prize in the US.