---
title: "Lab 03 - Nobel laureates"
author: "Annie Somerville"
date: "02.10.21"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r glimpse, message=FALSE}
glimpse(nobel)
```
This data has 935 observations/nobel laureates and 26 variables.

### Exercise 2


#### r nobel_living
``` {r nobel_living}
nobel_living <- nobel %>%
  filter (
    is.na(died_date) &
    !is.na(country_original) &
    gender != "org"
  )
glimpse(nobel_living)
```

I used the `r glimpse(nobel_living)` code above to filter for people opposed to organizations, those who are still living, and those who had available countries.

### Exercise 3

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...
