---
title: "Lab 03 - Nobel laureates"
author: "Annie Somerville"
date: "02.10.21"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
nobel <- read_csv("data/nobel.csv")
```

## Exercises

### Exercise 1

```{r glimpse, message=FALSE}
glimpse(nobel)
```
This data has 935 observations/nobel laureates and 26 variables.

### Exercise 2


#### r nobel_living
``` {r nobel_living}
nobel_living <- nobel %>%
  filter (
    is.na(died_date) &
    !is.na(country_original) &
    gender != "org"
  )
glimpse(nobel_living)
```

I used the `r glimpse(nobel_living)` code above to filter for people opposed to organizations, those who are still living, and those who had available countries.

### Exercise 3

``` {r country_us}
nobel_living <- nobel_living %>%
  mutate(
    country_us = if_else(country == "USA", "USA", "Other")
  )
```

``` {r nobel_living_science}
nobel_living_science <- nobel_living %>%
  filter(category %in% c("Physics", "Medicine", "Chemistry", "Economics"))
```


``` {r barplot}
ggplot(data=nobel_living_science, aes(x=category, fill=country_us)) +
geom_bar(stat="count", position=position_dodge()) +
  coord_flip()
```

Winners of science prizes were much more likely to be in the US than other countries, so I would say that Buzzfeed's article headline is seems accurate.


### Exercise 4

``` {r born_country_us}
nobel_living_science <- nobel_living_science %>%
  mutate(
    born_country_us = if_else(born_country == "USA", "USA", "Other")
  )

nobel_living_science %>%
  count(born_country_us)
```

636 of the winners were not born in the US, and 271 winners were born in the US. Out of the science winners, 123 were born outside the US and 105 were born in the US.

### Exercise 5

``` {r barplot2}
ggplot(data=nobel_living_science, aes(x=category, fill=country_us)) +
geom_bar(stat="count", position=position_dodge()) +
  coord_flip()
```

### Exercise 6

...
